Examples of functions

### 2024-06-05 ExPro.Rmd
updated version

To install the package the following line of code is needed.

@@

Four our examples on real data we used prom the package 'psych' the dataset "holzinger.swineford" which has a series of demografics and scores of different subtests measuring intelligence. Once the package is retrieved with the 'library' command, the dataset can be opened using the 'data' function. For simplicity we decided to rename it with a shorter name.

@@

#### Critical value for correlation from a cor.test object

In the following chunk we want to get the critical value for a correlation of two cognitive tests of 301 subjects. We can do so with the 'critical' function:

@@

First, the 'cor.test' function should be used on the two variables of interest and then the newly created object should be put into the 'critical' function. The output will add, underneath the usual output of the 'cor.test' function, the absolute critical value (rc). The number represents the smallest significant effect.

#### Critical value for t-test from real data

Now we want to know the critical value for a t-test comparing boys and girls on a cognitive variable of visual perception, as we assume gender differences. In this case, it can be easily done with the same procedure using the 't.test' function:

@@

#### Critical value for linear model from real data

@@

In the output, a column will appear next to the usual column of the Estimates reporting critical values for both the Intercept and the predictor(s).

@@

The function requires to specify the hypothesis as "less", "greater" or "two.tailed". In output we can find the critical d and the critical g, the adjusted d for small samples.

@@

Specifying the direction of the hypothesis and the confidence interval, the function will give as output the standardized and un-standardized critical cohen's d, and the critical cohen's d adjusted for small samples both standardized and un-standardized.

#### Critical value for a correlation

@@

#### Critical value of a beta from a model

>>>>

To install the package the following line of code is needed:

@@

For our examples on real data we used from the package 'psych' the dataset "holzinger.swineford" which has a series of demographics and scores of different subtests measuring intelligence on 301 subjects. Once the package is retrieved with 'library', the dataset can be opened using 'data("name of the dataset")'. For simplicity we decided to rename it with a shorter name.

@@

#### Critical value for correlation

In the following chunk we want to get the critical value for a correlation of two cognitive sub-tests of 301 subjects. We can do so with the 'critical' function:

@@

First, the 'cor.test' function should be used on the two variables of interest and then the newly created object should be put into the 'critical' function. The output will add, underneath the usual output of the 'cor.test' function, the absolute critical value (rc), representing the smallest significant effect.

#### Critical value for t-test

Now we want to know the critical value for a t-test comparing boys and girls on a cognitive variable of visual perception. In this case, it can be easily done with the same procedure using the 't.test' function:

@@

#### Critical value for linear model

@@

In the output, a column will appear next to the usual column of the estimates reporting critical values for both the intercept and the predictor(s).

@@

The function requires to specify the hypothesis as "less", "greater" or "two.tailed". In output we can find the critical d and the critical g, which is the cohen's d adjusted for small samples.

@@

Specifying the direction of the hypothesis and the confidence interval, the function will give as output the standardized (dzc) and un-standardized (dc) critical cohen's d, and the critical cohen's d adjusted for small samples both standardized (gc) and un-standardized (gzc).

#### Critical value for a correlation from sample size

@@

#### Critical value of a beta from a model from saple size
